Statically Typed String Sanitation Inside a Python

### 2014-08-19 sanitation-psp14/sanitation-psp14-short.tex
Updated description.

 \textsc{S-T-SafeCoerce}: \todo{fix this description} allows only safe coercions between string types by
    expoiting the decidability of language inclusion.

\textsc{S-T-Check}: \todo{fix this description}The check rules allow casts between strings that cannot be guaranteed at compile time, but might pass a runtime check.

\subsubsection{Replacement}

>>>>

The $\lambdas$ language supports two forms of coercion. Safe coercion only allows coercsion between 
strings types which are guaranteed to be safe. This form of coercion is useful because the replacement operation (introduced below in Section~\ref{sec:replace}) is often more conservative than absolutely necessary.
Conversely, unsafe coercion -- which we refer to as a checked coercion -- 
allows for potential unsafe type casts. Our semantics for check ensures that only safe values are used. Whenever a value is determined to be unsafe at runtime, a default value $e_2$ is used instead.

Summarily, 
 \textsc{S-T-SafeCoerce} allows only safe coercions between string types by
    expoiting the decidability of language inclusion, while
\textsc{S-T-Check} allows casts between strings that cannot be guaranteed at compile time, but inserts a runtime check a runtime check.

\subsubsection{Replacement}\label{sec:replace}
